---
title: "Lab 3 Report"
author: "Rose Lakeman"
date: "`r format(Sys.Date())`"
output: github_document
---

Instructions for this lab report can be found on [Your assignment section of Lab Assignment 3 Introduction to ggplot2](https://biol275-msum.github.io/introduction-to-ggplot2.html#your-assignment) on the lab website.

## Fireflies

> A. Insert an R code chunk and create a graph depicting the frequency distribution of the 35 mass measurements. It should have legible text and appropriate axis labels.

```{r}


# Load Packages ------------------------------------------------------------

library(tidyverse)

# Fireflies Data ----------------------------------------------------------

fireflies_data <- read_csv("https://whitlockschluter.zoology.ubc.ca/wp-content/data/chapter02/chap02q19FireflySpermatophoreMass.csv")

fireflies_data # print the data in the console

distinct(fireflies_data,spermatophoreMass) #view specific data

count(fireflies_data,spermatophoreMass) #displays values of specified variable in the console

ggplot(data = fireflies_data) +
  geom_histogram(mapping = aes(x = spermatophoreMass),
                 fill = "#C5351B", color = "black", binwidth = 0.008) +
  labs(x = "spermatophoreMass (mg)", y = "Frequency (spermatophoreMass)") +
  theme_classic() +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black", size = rel(1))
  ) #function to produce the histogram



```


> B. What type of graph did you choose in part (A)? Why?

Because we are only measuring one variable (spermatophore mass) using a histogram is a better way to display the data to be able to understand what it means.

> C. Describe the shape of the frequency distribution. What are its main features?

It is right skewed

> D. What term would be used to describe the largest measurement in the frequency distribution? You can refer to the lecture slides, your notes, or the textbook.

Mode

## Bird orders

I read the data using the code provided by the instructor. The dataset is from the auk package and was originally named ebird_taxonomy. I converted it to a tibble, removed non-species taxa, and named the new dataset birds.

```{r}
library(auk)                          # load the auk package
birds <- ebird_taxonomy %>%           # start with the ebird_taxonomy data
  as_tibble() %>%                     # tibbles print better in the console
  filter(category == "species")       # remove non-species taxa
```

> E. How many bird species are in the new birds dataset? How did you find out?

Count(birds, species) and that told me there was 10721 species

> H. How many orders are there? You can get this right by counting on the graph, but you will only get full points if you use some code to figure it out.

41, using distinct() and count()

> F. Insert an R code chunk and create a graph depicting the distribution of orders in the birds dataset. Sort the orders with the most frequent on the left. It should have legible text and appropriate axis labels.

```{r}


# Load Packages -----------------------------------------------------------

library(tidyverse)

# ebird Taxonomy ----------------------------------------------------------

library(auk)                          # load the auk package
birds <- ebird_taxonomy %>%           # start with the ebird_taxonomy data
  as_tibble() %>%                     # tibbles print better in the console
  filter(category == "species")       # remove non-species taxa

distinct(birds, order) #displays the variety of orders possible in the console
count(birds, order)   #displays the different orders with the amount in each order 

ggplot(data = birds) + 
  geom_bar(mapping = aes(x = fct_infreq(order)), fill = "#C5351B") +
  labs(x = "Order", y = "Frequency (number of species)") +
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = 0)) +
  theme_classic(base_size = 7) +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.ticks.x = element_blank()
  ) #functions that displays the bar graph, specifying the x and y axis

                         

                         
```


> G. What kind of graph did you create? Why?

Bar graph because we are measuring the frequency of multiple different types of birds (categorical data). We can see that there is a lot more species of Passeriformes than any other order

## Links to peer review

I reviewed Hiba Chaudhry's lab report at this URL: https://github.com/BIOL275-MSUM/lab-3-intro-to-ggplot-gt3637ut/issues/2

Hiba Chaudhry reviewed my lab report at this URL: https://github.com/BIOL275-MSUM/lab-3-intro-to-ggplot-rlakemn517/issues/1

## Session Info

Here is my session information:

```{r}
sessioninfo::session_info()
```
